%!TEX root = main.tex
\paragraph{Statement of principal findings}
    We estimate that $R_{0c}>1$ and  $R_{0h}<1$. Thus DHF cases, 
cannot sustain new DHF cases. Furhter, $R_{0h}<1$ imply an
exponential decay on the number of infected individuals. However,
a small DHF outbreak arises despite the value of $R_{0h}$, we deduce
that this DHF dynamics is a consequence of the
intensity of the outbreak of DF, given by serotype 2.

    We formulate a  model to describe the evolution of DCF and DHF
cases in Hermosillo for the 2010 outbreak and evaluate if ADE
hypotesis could explain the DHF dynamics. 
The central hypotheses of this manuscript were:
    \begin{itemize}
        \item
            strain DENV-II circulated in the 2010 Hermosillo 
        \item
            Dengue outbreak antibody-Dependent Enhancement hypothesis
            could explain the DHF high incidence 
        \item
            unconfirmed cases represent almost 95 \% of the total
            incidence.
    \end{itemize}
    With these hypotheses, we obtain a model that describes
the incidence dynamics of DHF cases of the 2010 Hemosillo outbreak.
Our parameters estimation does not reject these hypothesis and provide
statistical evidence that the concerning reproductive number is in the 
\num{95} \% confidence interval [\num{1.81253}, \num{2.134538}].

%
\paragraph{Strengths and weaknesses of the study} 
    Our $\mathcal{R}_0$ estimation is consistent with other outbreak reports [*].
To the best of our knowledge, this is the first attempt to fit the 
two exponential growth curves of the incidence according to Dengue 
Disease severity.  Furter, our reproductive numeber $\mathcal{R}_0$ 
results be the geometric mean of two expresion that are closed related 
with parameters transmition according to severity.  

    However, our formulation only considers an outbreak
of one season. Thus classical asymptotic analysis has mathematical 
consistency but lacks biological meaning.  In this line, we are preparing
a version that achieves both\textemdash proper data fitting and consistent
asymptotic behavior. We believe that adding a class of immunity according
to the particular strain would be an option.


     We take ideas from \citet{Zheng2018, Nuraini2007, Feng1997a} to modulate 
the propensity of acquire Dengue due to a given serotype.  
Our model describe DHF transmission with a certain probability.  
\todo{review: Mathematical Medicine and Biology: A Journal of the IMA, dqz013, https://doi.org/10.1093/imammb/dqz013}
Thus, combining this idea with the hypothesis of unreported 
incidence \cite{Li2013b,Guzman2002}, we achieve proper
data fitting via maximum likelihood estimation. 

    The cause of DHF is still unclear; for example, in \cite{ESTEVA2015} reports
that the concentration of the virus explains the severity of Dengue.
In this direction, Gomez et al. provide a model that considers a
severity stratification according to the mosquito load virulence.

    Our contribution describes scenarios wherein past Dengue
outbreaks detected a dominant  strain. Then decision-makers could
project new dengue strain invasion scenarios. Thus, we believe that early 
serotype identification in any Dengue outbreak would be essential to  
make epidemiological decisions.

    In short, our contribution sugest that early serotype identification in any Dengue
outbreak would be essential infromation to make epidemiological decisions.

