\documentclass[draft, openbib]{imammb}
\jno{dqnxxx}
\usepackage[english]{babel}
\usepackage[pagebackref=true]{hyperref}
\usepackage{doi}
\usepackage{amsmath, amsthm, bm, mathrsfs}
\input{standard}
\usepackage{bbold}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{caption}
\usepackage{siunitx}
\usepackage{xspace}
\usepackage{color}
\usepackage{proba}
\usepackage{natbib}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{cleveref}
\usepackage{paralist}
% \usepackage[disable]{todonotes}
\usepackage[textwidth=1in, textsize=tiny]{todonotes}
\usepackage{bigints}
\usepackage[title,titletoc,toc]{appendix}
\usepackage{siunitx}
\usepackage{acro}
\input{setup}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={((},close={))}}
\newcommand{\tinytodo}[2][]
{\todo[caption={#2}, size=\tiny, #1]{
	\renewcommand{\baselinestretch}{0.5}\selectfont#2\par}
}
\renewcommand{\theequation}{\thesection.\arabic{equation}}
\numberwithin{equation}{section}
\def\citeasnoun{\cite}
%
\begin{document}
    \title{
        Modeling and $R_0$ estimation  of the 2010 Dengue Hemorrhagic Fever 
        Outbreak in Hermosillo Sonora.
    }    
    \author{%
            {\sc S. D\'{\i}az-Infante%
                \footnote{Corresponding author. 
                    Present address: Departamento de Matem\'aticas, Universidad de Sonora
                    Blvd. Rosales y Luis Encinas S/N, Col. Centro, Hermosillo, Sonora, C.P. 83000,
                    M\'exico. Email: saul.diazinfante@unison.mx
                }
            }\\[2pt]
        CONACYT-Universidad de Sonora,
        Departamento de Matem\'aticas, Universidad de Sonora\\[6pt]
        Blvd. Rosales y Luis Encinas S/N, Col. Centro, Hermosillo, Sonora, C.P. 83000,
        M\'exico\\ 
        {\sc J. A. Montoya Laos 
            \footnote{Email: montoya@unison.mx}
        }\\[2pt]   
        Universidad de Sonora,
        Departamento de Matem\'aticas, Universidad de Sonora\\[6pt]
        Blvd. Rosales y Luis Encinas S/N, Col. Centro, Hermosillo, Sonora, C.P. 83000,
        M\'exico\\ 
        %
        { \sc and
            \\
             D. Olmos Liceaga 
            \footnote{Email: daniel.olmos@unison.mx}
        }\\[2pt]   
        Universidad de Sonora,
        Departamento de Matem\'aticas, Universidad de Sonora\\[6pt]
        Blvd. Rosales y Luis Encinas S/N, Col. Centro, Hermosillo, Sonora, C.P. 83000,
        M\'exico\\ 
        {\rm [\today]}\vspace*{6pt}
    }
    
    \pagestyle{headings}
    \markboth{S. D\'{\i}az-Infante, J. A. Montoya Laos and D. Olmos Liceaga }{\rm 
        Modeling and $\mathcal{R}_0$ estimation of the 2010 Dengue Hemorrhagic Fever Outbreak in Hermosillo Sonora}
    \maketitle
    \begin{abstract}
        {We model and estimate the basic reproductive number of Dengue  and 
        Dengue Hemorrhagic Fever outbreak of the 2010 from Hermosillo Sonora.
        Our results suggest that serotype DENV-2 of the Dengue virus and the cross 
        infection risk enhancement hypothesis, could explain the incidence of
        Dengue Hemorrhagic Fever cases reported by Secretaria de Salud del Estado de 
        Sonora.}
        {Differential Equations;
        Dengue Hemorrhagic Fever; 
        Boot strap;}
    \end{abstract}

    \section{Introduction} \label{intro}
        State the objectives of the work and provide an adequate 
        background, avoiding a detailed literature survey or a 
        summary of the results.

        \paragraph{Objectives}
        Our objective is to explain the dengue hemorrhagic outbreak that 
     occurred in the city of Hermosillo, located in the state of Sonora in 2010.
    %
    \paragraph{Severity}
    \ac{DCF} 
    \ac{DHF} description.
    \paragraph{ADE hypothesis}
     \ac{DENV-1}, \ac{DENV-2}
     reinfection as cause of hemorrhagic.
        \paragraph{Background}
            It was reported that in 2010 there was present only DENV-1 circulating
        Hermosillo (Tesis de Pablo. La referencia que menciona ya no se encuentra
        disponible por internet.)  
        \section{Material and methods}
        Provide sufficient detail to allow the work to be 
        reproduced, with details of supplier and catalogue 
        number when appropriate. Methods already published 
        should be indicated by a reference: only relevant 
        modifications should be described.
        \subsection{Data}
            \label{sec:Intro}
            \paragraph{Data description (Pablo)}
            \input{data_description.tex} % Pablo
            \paragraph{Socioeconomic description: 
                homogeneity according to population density index}
        \input{socioeconomic_homogenety.tex} % Ana-Lucia
        \subsection*{Model}
            \input{model_introduction.tex}
      \input{main_hypothesis.tex} % Daniel
            \input{twoStrainsModel.tex}
            \input{tableParameters.tex}
        \subsection{$R_0$ estimation (Montoya)}
        We suppose that the number of cases of classic and hemorrhagic
        dengue are observed at time points $t_{1}, \dots , t_{n}$.
        Here we assume that these processes, denoted by $X_{t}$ and
        $Y_{t}$ respectively, follow a Poisson distribution with mean
        $\lambda_{h}\left(t\right)=Y_{-1}^{[h]}$ and
        $\lambda_{c}\left(t\right)=Z$, where
            \input{data_analysis.tex} % Montoya
            \input{estimation.tex}    % Montoya
        In our case the vector of parameters of the ordinary differential
        equations model is $\phi=\left(\phi_{1},\phi_{2}\right)$, where
        $\phi_{1}=\left(\beta_{H},\beta_{M}\right)$ is regarded as unknown and
        $\phi_{2}=\left(\alpha_{c},\alpha_{h},b,\mu_{H},\mu_{M},\sigma,\theta,p\right)$
        is known in advance. We write $\lambda_{h}\left(t\right)$ and
        $\lambda_{c}\left(t\right)$ as $\lambda_{h}\left(t;\phi_{1}\right)$
        and $\lambda_{c}\left(t;\phi_{1}\right)$ to emphasize this fact.
 
        We use the likelihood approach to estimate the vector
        parameter  $\psi_{1}$ based on the observed samples
        $\vec{x}=\left(x_{t_1}, \dots , x_{t_n} \right)$ and
        $\vec{y}=\left(y_{t_1} \dots , y_{t_n} \right)$. The resulting
        likelihood function is thus

    \begin{equation}
        \begin{split}
            L \left( \phi_{1} \right)
             &= \prod_{i = 1} ^ {n} 
             \left \{ 
                 \frac{1}{x_{t_i}!}
                     \left[\lambda_{h}
                         \left(t_{i};\phi_{1}\right)
                     \right] ^ {x_{t_i}} \exp
                     \left[
                         \lambda_{h} \left(t_{i}; \phi_{1} \right)
                     \right] 
             \right. 
            % \\
            % & \quad \quad \quad
            \left.
                 \frac{1}{y_{t_i}!}
                 \left[\lambda_{c}
                     \left(t_{i};\phi_{1}\right)
                 \right] ^ {y_{t_i}}
                 \exp
                 \left[
                     \lambda_{c}
                     \left(t_{i};\phi_{1}\right)
                 \right]
             \right\}.\label{LikFun}
        \end{split}
    \end{equation}
    The maximum likelihood estimate (MLE) of $\phi_{1}$ is that value 
    of $\phi_{1}$ that maximizes $L\left(\phi_{1}\right)$ in 
    \eqref{LikFun}. We denote the MLE of $\phi_{1}$ as $\hat{\phi}_{1}$.

        We now consider profile-likelihood inference based on (1) for
    estimating the parameters of interest ($R_{01}$, $R_{02}$, and
    $\mathcal{R}_{0}$). Here we assume without loss of generality that
    $\phi_{1}=\left(\beta_{H},\beta_{M}\right)$ can be rewritten as
    $\phi_{1}=\left(\gamma,\eta\right)$, where $\gamma$ is a scalar
    parameter of interest and $\eta$ is a scalar nuisance parameter. For
    example, we may only be interested in $R_{01}$. In this case, we can
    rewrite the parameter $\beta_{M}$ as a function of the parameters
    $R_{01}$ and $\beta_{H}$, 
    \begin{equation}
        \beta_{M}=C\frac{R_{01}}{\beta_{H}}, \nonumber
    \end{equation}
    where
    \begin{equation}
        C=\left[\left(\frac{N_H - N_{S_{-1}}}{\alpha_c + \mu_H}
            +\frac{(1- \theta ) \sigma N_{S_{-1}}}{ \alpha_c + \mu_H}\right)
            \left(\frac{b^2\Lambda_M}{\mu_M ^ 2  N_H ^ 2}\right)\right]^{-1} \nonumber
    \end{equation}
        Thus, we reparametrize the model in terms of 
    $\phi_{1}=\left(\gamma,\eta\right)=\left(R_{01},\beta_{H}\right)$, 
    where $\gamma=R_{01}$ is the parameter of interest and 
    $\eta=\beta_{H}$ is the nuisance parameter.

        The profile likelihood and its corresponding relative likelihood
    function of $\gamma$, standardized to be one at the maximum of the
    likelihood function, are 
    \begin{equation}
        \begin{split}
            L_{\max}
                \left(
                \gamma\right)&=\max_{\eta}L\left(\phi_{1}=\left(\gamma,\eta \right)
            \right),  \nonumber \\
            R_{\max}
            \left(
                \gamma\right)   
                &=  
                    \frac{L_{\max}\left(\gamma\right)}{\displaystyle\max_{\phi_{1}}L\left(\phi_{1}\right)},
        \end{split}
\end{equation}
where $L\left(\cdot\right)$ is the likelihood function given in
(\ref{LikFun}). In particular, the relative profile likelihood varies between
0 and 1 and ranks all possible $\gamma$ values based only on the observed
samples $\vec{x}=\left(x_{t_1}, \dots , x_{t_n} \right)$ and
$\vec{y}=\left(y_{t_1} \dots , y_{t_n} \right)$. Thus, a graph of
$R_{\max}\left(\gamma\right)$ allows to distinguish plausible and implausible
values for $\gamma$.

A level $\omega$ profile likelihood region (commonly an interval) for $\gamma$ is given by
\begin{equation}
\left\{\gamma: R_{\max}\left(\gamma\right) \geq \omega \right\}, \nonumber
\end{equation}
where $0 \leq \omega \leq 1$. We can assign a confidence level to the
profile likelihood region of $\gamma$  considering the asymptotical
behavior of the likelihood ratio statistic
$D=-2\ln{R_{\max}\left(\gamma_{0}\right)}$. This is an asymptotic
pivotal quantity having a Chi-squared distribution with one degree of
freedom. Thus, approximate confidence levels of $99\%$, $95\%$ and
$90\%$ can be ascribed to profile likelihood regions at $\omega$ =
0.036, 0.146, and 0.25, respectively.
\section{Results}
        Results should be clear and concise.
        \paragraph{Modeling Results (Saúl-Daniel)}

\paragraph{Data analysis (Saúl-Montoya)}
        \paragraph{$R_0$ and parameter inference (Montoya)}

\section{Discussion}
        This should explore the significance of the results of 
    the work, not repeat them. A combined results and 
    Discussion section is often appropriate. Avoid extensive 
    citations and discussion of published literature.

        In our results we obtained $R_{0c}>1$ and  $R_{0h}<1$. This means
    that for this outbreak, the presence of DHF cases, cannot trigger
    on its own new DHF cases and in general, $R_{0h}<1$ would imply an
    exponential decay on the number of infected individuals. However,
    the small DHF outbreak arises despite the value of $R_{0h}$ as
    there is an increase in infected mosquitoes of the serotype 2 due
    to the presence of the $S$ individuals, which initially is close
    to $N_S$. Therefore, DHF dynamics is a consequence of the
    intensity of the outbreak of DF, given by serotype 2. 
    
    
    
    \section{Conclusions}
        The main conclusions of the study may be presented in a 
    short Conclusions section, which may stand alone or form 
    a subsection of a Discussion or Results and Discussion 
    section.
    
        In this work we have presented a mathematical model to understand
    the 2010 dengue outbreak that occurred in Hermosillo, Mexico. The
    model includes infected classes of classic and hemorrhagic
    versions of dengue in order to adjust the observed data. To our
    knowledge, there is no published work
    \bibliography{Epidemiology-TrabajoConDaniel}
\end{document}
